Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging

### 2020-06-25 cover_letter.tex
Swap to just using {letter} template for cover letter
Fixed quotation marks around article title

\documentclass[12pt,stdletter,orderfromtodate,dateleft,sigleft]{newlfm}
\usepackage[hidelinks]{hyperref}

\topmarginsize{0in}
\topmarginskip{0in}
\headermarginsize{0in}
\headermarginskip{0in}

\leftmarginsize{1in}
\rightmarginsize{1in}

\newlfmP{addrfromskipbefore=0pt}
\newlfmP{addrfromskipafter=0pt}

\newlfmP{sigskipbefore=10pt}
\newlfmP{sigsize=40pt}

\newlfmP{Headlinewd=0pt,Footlinewd=0pt}

\namefrom{Colin Sullender, Ph.D.}
\addrfrom{%
    Colin Sullender\\
    The University of Texas at Austin\\
    Department of Biomedical Engineering\\
    107 W. Dean Keeton Street, Stop C0800\\
    Austin, TX, 78712, USA
}

\dateset{\today}

\greetto{Dear Dr. Boas,}

\closeline{Sincerely,}

\begin{document}
\begin{newlfm}

We wish to submit a new manuscript entitled ''Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging'' for consideration by \emph{Neurophotonics}. We confirm that this work is original and has not been published elsewhere nor is it currently under consideration in another journal.

@@

\end{newlfm}
\end{document}

>>>>

\documentclass[12pt]{letter}
\usepackage[a4paper]{geometry}
\usepackage[hidelinks]{hyperref}

\name{Colin Sullender}
\address{
    Colin Sullender\\
    The University of Texas at Austin\\
    Department of Biomedical Engineering\\
    107 W. Dean Keeton Street, Stop C0800\\
    Austin, TX, 78712, USA
}
\signature{\vspace{50pt} Colin Sullender, Ph.D.}
\longindentation=0pt

\begin{document}
\begin{letter}{}

\opening{Dear Dr. Boas,}

We wish to submit a new manuscript entitled ``Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging'' for consideration by \emph{Neurophotonics}. We confirm that this work is original and has not been published elsewhere nor is it currently under consideration in another journal.

@@

\closing{Sincerely,}

\end{letter}
\end{document}
